Modeling Intervention Strategies for United States TB Control

### 2014-02-15 in_progress/presentations/paper/draft.tex
Starting results

\section{Results}
\subsection{Basic Population Breakdown}
The additional tracking capabilities offered several key insights into US TB
dynamics. Figure~\ref{fig:incPlotSourced} shows the yearly incidence of US TB, broken
down into infection source. It can be seen that the majority of the US TB load
is driven by activations of FB LTBI, followed by USB LTBI activations. This data
further agrees with the conclusions drawn by Hill, Becerra, and Castro about the
necessity of LTBI treatment in any valuable intervention strategy. 
\begin{figure}[h]
  \begin{center}
    \includegraphics[scale=.5]{incPlotSourced}
  \end{center}
  \caption{Sourced yearly incidence data generated by the extended Hill Model.}
  \label{fig:incPlotSourced}
\end{figure}
Further, figure~\ref{fig:costPlotSourced} shows a similarly sourced plot, but analyzing the
final US HCS costs due to TB. One can see that in this plot, roughly half of the
US TB HCS costs are due to activations of LTBI. In this data, it is appropriate
to think of the costs due to acute LTBI are due to exogenous re-inection,
whereas active TB costs due to chronic LTBI are activations of LTBI into active
TB. 
\begin{figure}[h]
  \begin{center}
    \includegraphics[scale=.35]{costPlotSourced}
  \end{center}
  \caption{Sourced US HCS economic TB load. Note that this data only illustrates
    the load due to treating active TB, but illustrates where the infections
    driving this cost come from.}
  \label{fig:costPlotSourced}
\end{figure}
Note that both of these plots underestimate the impact LTBI activations play in
the spread of TB, as every LTBI activation to infectious TB contributes not only
to incidence and costs directly, but also indirectly by causing additional
future cases, which is not captured in these graphs. Further, there is also US
HCS costs due to treating LTBI, which is not illustrated in these graphs. 
\subsubsection{Basic Reproduction Number}
The basic reproduction number of FB or USB cases of infectious TB was also
estimated by this system. Using the best-fit values of parameters from the 
Hill model, we found the average number of secondary infections arising from
a single case of infectious TB to be 0.423 and 0.370 for USB and FB populations
respectively.  These values differ because in the model, there are different
estimates for death rates and the rate of TB treatment and self-cure in the USB and FB populations, 
so the average infectious period differs between the two populations.
Extrapolating these results, we can think of the
total number of secondary infections over 100 years due to a FB or USB
infectious TB case as describing a geometric series in a large population.
Presuming there are no overlaps in infectious contacts, if a single case of
infectious TB in either population infects $p_f, p_u$ new cases,
respectively, then we can say that over the course of 100 years, the total
number of cases infected will follow a geometric series. This analysis predicts
that over 100 years, one USB infection will lead to $1.04$ subsequent infections,
whereas one FB infection will lead to $.83$ subsequent infections. Experimentally, 
these data were also analyzed, with results of $1.03$ and $.64$, respectively. 
Full calculations are included in the Appendix.

>>>>

\section{Results}
\subsection{Basic Population Breakdown}
The additional tracking capabilities offered several key insights into US TB
dynamics. Figure~\ref{fig:incPlotSourced} shows the yearly incidence of US TB, broken
down into infection source. It can be seen that the majority of the US TB load
is driven by activations of FB LTBI, followed by USB LTBI activations. This data
further agrees with the conclusions drawn by Hill, Becerra, and Castro about the
necessity of LTBI treatment in any effective intervention strategy. 
\begin{figure}[h]
  \begin{center}
    \includegraphics[scale=.5]{incPlotSourced}
  \end{center}
  \caption{Sourced yearly incidence data generated by the extended Hill Model.}
  \label{fig:incPlotSourced}
\end{figure}
Further, figure~\ref{fig:costPlotSourced} shows a similarly sourced plot, but analyzing the
final US HCS costs due to active TB. One can see that in this plot, roughly half
of the US TB HCS costs are due to activations of LTBI. Note that In this data,
it is appropriate to think of the costs due to acute LTBI as costs due to
exogenous re-inection, whereas active TB costs due to chronic LTBI are
activations of long standing latent infections into active TB. 
\begin{figure}[h]
  \begin{center}
    \includegraphics[scale=.35]{costPlotSourced}
  \end{center}
  \caption{Sourced US HCS economic TB load. Note that this data only illustrates
    the load due to treating active TB, but illustrates where the infections
    driving this cost come from.}
  \label{fig:costPlotSourced}
\end{figure}
Note that both of these plots underestimate the impact LTBI activations play in
the spread of TB, as every LTBI activation to infectious TB contributes not only
to incidence and costs directly, but also indirectly by causing additional
future cases, which is not captured in these graphs. Further, there is also US
HCS costs due to treating LTBI, which is not illustrated in these graphs. 
\subsubsection{Basic Reproduction Number}
The basic reproduction number of FB or USB cases of infectious TB was also
estimated by this system. Using the best-fit values of parameters from the 
Hill model, we found the average number of secondary infections arising from
a single case of infectious TB to be 0.423 and 0.370 for USB and FB populations
respectively.  These values differ because in the model, there are different
estimates for death rates and the rate of TB treatment and self-cure in the USB and FB populations, 
so the average infectious period differs between the two populations.
Extrapolating these results, we can think of the
total number of secondary infections over 100 years due to a FB or USB
infectious TB case as describing a geometric series in a large population.
Presuming there are no overlaps in infectious contacts, if a single case of
infectious TB in either population infects $p_f, p_u$ new cases,
respectively, then we can say that over the course of 100 years, the total
number of cases infected will follow a geometric series. This analysis predicts
that over 100 years, one USB infection will lead to $1.04$ subsequent infections,
whereas one FB infection will lead to $.83$ subsequent infections. Experimentally, 
these data were also analyzed, with results of $1.03$ and $.64$, respectively. 
Full calculations are included in the Appendix.
